Towards Automated Merging of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-05-06 sattose/paper.tex
Updates from Overleaf

Comparing it to the results of Fontana et al. \cite{fontana2015duplicated}, we find way more unrelated clones. This might be due to the fact that we consider clone classes rather than clone pairs, and mark the clone class ``Unrelated'' even if just one of the clone instances is outside a hierarchy. It could also be that the corpus which we use, as it has generally smaller projects, uses more classes from outside the project (which are marked ``Unrelated'' if they do not have a common external superclass). On the second place, we have the ``Same Class'' clones. On the third place come the ``Sibling'' clones.

@@

Unsurprisingly, most clones span a part of a method. Just 1.6\% of the methods are cloned fully. More than a quarter of the clones spans over several methods, which is surprising. Simply extracting methods won't work in a case where a clone spans over several methods. About 4.5\% of clones include a constructor. About 3.3\% of clones include a global variable defined in a class.

>>>>

Comparing it to the results of Fontana et al. \cite{fontana2015duplicated}, we find way more unrelated clones. This might be due to the fact that we consider clone classes rather than clone pairs, and mark the clone class ``Unrelated'' even if just one of the clone instances is outside a hierarchy. It could also be that the corpus which we use, as it has generally smaller projects, uses more classes from outside the project (which are marked ``Unrelated'' if they do not have a common external superclass). About a fourth of all clone classes have all instances in the same class, which is generally easy to refactor. On the third place come the ``Sibling'' clones, which can often be refactored using a pull-up refactoring.

@@

Unsurprisingly, most clones span a part of a method. Just 1.6\% of the methods are cloned fully. More than a quarter of the clones spans over several methods, which makes extracting methods won't work in a case where a clone spans over several methods. About 4.5\% of clones include a constructor. About 3.3\% of clones include a global variable defined in a class.
